### 2014-02-17 proposal/new_proposal.tex
New introduction.

\section*{Introduction}
For any large retailer, it is valuable to know the relationship between
products they sell or could sell. This information can be used to build
recommendations for similar products, understand subsets of products that
appeal to certain users, or expand a catalogue to include new products that
will be liked by the existing user-base. Currently, many retailers already
leverage user traffic and content information to learn these relationships
within their catalogue. However, in spaces where competing retailers sell many
of the same products, such as department stores or movie vendors, more
information can be gleaned by examining the inter-product relationships that
competing retailers have built for their own catalogues.

In this paper, we focus on department stores. This space is well suited for our
analysis since there are a number of competing stores with overlapping
catalogues. We model the relationships between products with a
\emph{recommendation graph}, which is a directed graph between the products in
a catalogue. A directed edge from product A to product B means that if a user
likes product A, he/she is likely to like product B. First we construct the
recommendation graphs of different department stores using the recommendations
given for each product on their websites. With these original graphs, we aim to
add meaningful edges within one retailer's graph (representing a new
recommendation) and between different retailer graphs (representing a candidate
to add to a catalogue).

We compare three approaches to extending the recommendation graphs. The first
approach is a baseline that uses a content-driven similarity function to add
edges between items. It ignores any information from the original
recommendation graphs. The second approach focuses exclusively on the
recommendation graphs. This method uses an identity function to determine which
items in different graphs are the same and thus links the graphs together.
Using a random walk algorithm, we determine which unlinked items should be
linked. The third approach is uses a combination of the first two to leverage
both kinds of information.

\section*{Data}
We collect the data by scraping the websites of major departments stores for
products with their descriptions, prices, photos, etc. From each product page,
we also gather the website's top recommended items for that product.  For this
paper, we scraped the catalogues of Macy's, Bloomingdale's, etc.  Each of these
websites requires their own scraper, but the same data is accessible from all
of them, including at least four recommended products for each product in the
catalogue. This allows us to build a directed recommendation graph for each
department store.

@@

\section*{Methods}
\subsection*{Method 1}
Create similarity scores between items. If items are similar, we add edges in
both directions to the recommendation graph. To determine the threshold of how
high the score must be before adding an edge, we calculate the average
similarity between items that are connected in the original graph.  These edges
can connect two items in the same catalogue or items across catalogues.

>>>>

\section*{Introduction}
A key challenge in retail is choosing which items to incorporate into one's
collection of offered goods and services. These decisions can significantly
impact a retailer's revenue in the short run as well as effect customer
experience, and hence, their relationship with the retailer. Several factors
must be considered including the number of product lines, the vareity of
products in each line, as well as the consistency and relationships between
products. In this study, we focus on the latter and explore techniques that
leverage publicly available product recommendation information for the purpose
of improving product assortment decisions.

It has become standard practice for online retailers to recommend one or more
products to prospective customers who have viewed or purchased an item. These
recommendations are generally derived from collaborative filtering or other
data-mining techniques employed by the retailer or a third-party service
provider. Importantly, these recommendations provide a source of publicly
available business intelligence by relating the items in their catalogue.
Specifically, these online recommendations logically form a directed graph in
with the vertices are products and an edge pointing from item A to item B
indicates that customers who view or purchase item A are recommended item B.
Given the recommendation graphs of two or more distinct retailers, our goal is
to determine new, meaningful edges that connect these graphs in a way that would
allow one retailer to relate their products to those of another retailer.

In this study we choose to focus on department stores, which typically have
overlapping product catalogues. We intend to exploit this overlap by identifying
identical inter-retailer products in order to achieve some initial connectivity
between their recommendation graphs. From there, we will explore and compare a
vareity of techniques for choosing additional edges to further connect these
originally disconnected graphs. In addition to relating {\em inter-retailer} items, we
are also interested in leveraging other retailer's recommendation graphs in
order to determine new {\em intra-retailer} edges, which can be valuable for
improving customer recommendations.

\section*{Data}
We collect the data by scraping the websites of major departments stores for
products with their descriptions, prices, photos, etc. From each product page,
we also gather the website's top recommended items for that product.  For this
paper, we scraped the catalogues of Bloomingdale's, Neiman Marcus, Nordstrom,
etc.. Each of these websites requires their own scraper, but the same data is
accessible from all of them, including at least four recommended products for
each product in the catalogue. This allows us to build a directed recommendation
graph for each department store.

@@

\section*{Methods}
We compare three approaches to extending the recommendation graphs. The first
approach is a baseline that uses a content-driven similarity function to add
edges between items. It ignores any information from the original
recommendation graphs. The second approach focuses exclusively on the
recommendation graphs. This method uses an identity function to determine which
items in different graphs are the same and thus links the graphs together.
Using a random walk algorithm, we determine which unlinked items should be
linked. The third approach is uses a combination of the first two to leverage
both kinds of information.

\subsection*{Method 1}
Create similarity scores between items. If items are similar, we add edges in
both directions to the recommendation graph. To determine the threshold of how
high the score must be before adding an edge, we calculate the average
similarity between items that are connected in the original graph.  These edges
can connect two items in the same catalogue or items across catalogues.
